### 2016-11-23 Chapters/experiments.tex
Remove commentary on section 3

\chapter{Monitoring of Gene Expression Machinery during growth transitions}

Missing results as of today:
\begin{itemize}
\item manual segmentation of one well --> mean RFU per pixel per cell (2-3 days in the best case, it could be difficult to export schnitzcells data)
\item semi-manual tracking of cells based on segmentation (hard to evaluate, will depend on schnitzcells performances, not optimistic)
\item estimation of $\alpha$ and $\mu$ over time (2-3 days for calculation, 2-3 days for implementation). I need tracking for $\mu$, maybe not for $\alpha$
\item make another experiments glu-sugar-glu (glycerol?), depends on Irina
\item analyze this experiments (repeat steps above, will probably be faster if we manage to work everything out, but still takes time because it's manual)
\item model modification to take into account the new data (5 days)
\end{itemize}

What could go wrong: everything. In particular:
\begin{itemize}
\item segmentation results could be impossible to export
\item tracking might not work (schnitzcells not designed to handle massive cell disappearance)
\item $\mu$ might be too noisy due to pixel size (note: image interpolation before segmentation might be a solution)
\item what we saw on the rough analysis might just be an artefact (as Hans usually says "When it works the first time, something went horribly wrong.")
\item the second experiment might not work (poor preculture, device plugged, out of focus overnight, medium contamination...)
\end{itemize}

Would everything go right, the chapter/article would be as follow.

@@

\subsection{Data analysis}

>>>>

\chapter{Monitoring Gene Expression Machinery abundance during a glucose upshift}

@@

\subsection{Cell segmentation}

\subsection{Kalman smoothing}
